HealpixNet: Efficient spherical Convolutional Neural Network with Healpix sampling for cosmological applications

### 2018-07-19 scnn.tex
softmax

Neural networks are constructed as stacks of layers which sequentially transform the input data. Our architecture, pictured in \figref{architecture}, is composed of the following types of layers: graph convolutional (GC) layers, non-linearity, pooling (P), batch normalization (BN), statistical layer (ST), and fully connected (FC) layers. All GC and FC layers are always followed by a non-linearity. As such, we will not mention the non-linearity in the description of our architectures.

@@

A non-linear function $\sigma(\cdot)$ is always applied after a linear GC or FC layer. The rectified linear unit (ReLU) $\sigma(\cdot) = \max(\cdot, 0)$ is a common choice. That operation is point-wise, i.e., $\Y_{ij} = \sigma(\X_{ij})$.

@@

@@

All those parameters are learned during training via back-propagation of the error gradient.
The whole network is then optimized to minimize the loss function over the training data. The gradient w.r.t.\ all the parameters is computed by back-propagation, and the values are updated by stochastic gradient descent (SGD).
Describe the loss function.

>>>>

Neural networks are constructed as stacks of layers which sequentially transform the input data. Our architecture, pictured in \figref{architecture}, is composed of the following types of layers: graph convolutional (GC) layers, non-linearity, pooling (P), batch normalization (BN), statistical layer (ST), and fully connected (FC) layers.

@@

% As such, we will not mention the non-linearity in the description of our architectures.
A non-linear function $\sigma(\cdot)$ is applied after every linear GC and FC layer, except for the last FC layer. That operation is point-wise, i.e., $\Y_{ij} = \sigma(\X_{ij})$. The rectified linear unit (ReLU) $\sigma(\cdot) = \max(\cdot, 0)$ is a common choice.

@@

The softmax layer is the last layer in a neural network engineered for classification. Given the output $\x \in \R^{N_{classes}}$ of the next to last layer, called the logits in the deep learning literature, the softmax layer outputs
\begin{equation*}
	y_i = \frac{\exp(x_i)}{\sum_{j=1}^{N_{classes}} \exp(x_j)} \in [0, 1], \ \forall i \in [N_{classes}],
\end{equation*}
where $N_{classes}$ is the number of classes to discriminate. Thanks to the softmax, the output $\y \in \R^{N_{classes}}$ of a neural network is a probability distribution over the classes, i.e., $y_i$ is the probability that the input sample belongs to class $i$. That last layer is actually normalizing $\x$ into $\y$ such that $\| \y \|_1 = \sum_i y_i = 1$.

@@

All those parameters are learned during training via back-propagation of the error gradient.
The whole network is then optimized to minimize the loss function over the training data. The gradient w.r.t.\ all the parameters is computed by back-propagation, and the values are updated by stochastic gradient descent (SGD).
Describe the loss function. It's a measure of how far the predictions $\y$ from the softmax are from the true labels $\b \delta_i$. KL-divergence.
